---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# pushoveR

<!-- badges: start -->
<!-- badges: end -->

{pushoveR} is an R API wrapper for [Pushover](https://pushover.net/).  API keys are needed to send push messages.

## Installation

Install the development version using {devtools}.

```{r, eval=FALSE}
# Install devtools if needed
#install.packages("devtools")

# Install g4sr using devtools
devtools::install_github("afsarchowdhury/pushoveR")
```

A [CRAN](https://cran.r-project.org/) version is unavailable at this time.

## Storing API keys

Store your API keys as environment variables in `.Renviron`.  That way, you can call them in `R` using `Sys.getenv()`.

Step 1: store your user key in `.Renviron` as, for example, `PO_U_KEY`.

```{r, eval=FALSE}
Sys.setenv("PO_U_KEY" = "thisISyourUSERkeyITlooksLIKEaLONGstringOFlettersANDnumbers")
```

Step 2: store your application key in `.Renviron` as, for example, `PO_R_KEY`.

```{r, eval=FALSE}
Sys.setenv("PO_R_KEY" = "thisISyourAPPLICATIONkeyITlooksLIKEaLONGstringOFlettersANDnumbers")
```

Step 3: restart your `R` session and test to make sure the keys have been added using the command

```{r, eval=FALSE}
Sys.getenv("PO_U_KEY")
```

You should see your user key printed in the console.  

Be aware: if you are using version control, you do not want to commit the `.Renviron` file in your local directory.  Either edit your global `.Renviron` file, or make sure that `.Renviron` is added to your `.gitignore` file.

## Sending push messages

A normal push message:

```{r normal, eval=FALSE}
pushoveR::send_push(
  token = Sys.getenv("PO_R_KEY"),
  user = Sys.getenv("PO_U_KEY"),
  title = "Hello",
  message = "This is a test message from pushoveR."
)
```

An emergency push message:

```{r emergency, eval=FALSE}
pushoveR::send_push(
  token = Sys.getenv("PO_R_KEY"),
  user = Sys.getenv("PO_U_KEY"),
  title = "Hello",
  message = "This is a test message from pushoveR.",
  priority = 2, # priority 2 is emergency priority
  retry = 30, # retry every 30 seconds
  expire = 300 # keep retrying for 300 seconds
)
```

## License

{pushoveR} is released on a [GPL-3 license](https://www.gnu.org/licenses/gpl-3.0.en.html).
